---
title: "Initial Coincept Draft"
author: "CN"
date: "`r format(Sys.Date())`"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning =  FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(echo = TRUE)
```

Here's the code that fetches the data: 

From the coincept repo `"code/get_data/fetch_coincept.R"`
```{r  eval=FALSE, echo=TRUE}
helpers = unique(fs::dir_info("code/functions/")$path)

walk(helpers, ~source(.x))

##now do em all 
coincept_metrics = c("txcount",
                        "txvolume(usd)",
                        "adjustedtxvolume(usd)",
                        "averagedifficulty",
                        "mediantxvalue(usd)",
                        "blocksize",
                        "blockcount",
                        "price(usd)",
                        "marketcap(usd)",
                        "exchangevolume(usd)")


coincept_data = map_df(coincept_metrics, function(metric){
  json = fetch_json(api_base = "https://coinmetrics.io/api/v1/",
                    endpoint = "get_asset_data_for_time_range",
                    first_parameter = "btc",
                    second_parameter = metric,
                    start_date = to_unix("year"),
                    end_date = to_unix("today")
  ) 
  
  out = 
    tibble(
      unix_date = tx_count %>% 
        flatten %>% 
        map_dbl(magrittr::extract2, 1),
      date_time = lubridate::as_datetime(unix_date),
      date = as.Date(date_time),
      year = str_extract(date, "^...."),
      month = str_extract(date, "(?=-)(.*)(?<=-)") %>% 
        str_remove_all(., "\\D"),
      day = str_extract(date, "..$"),
      result = tx_count %>% 
        flatten %>% 
        map_dbl(magrittr::extract2, 2),
      metric = paste0(metric)
    )

  return(out)  
})

saveRDS(coincept_data, "data/coincept_data.rds")

```

```{r data}
library(tidyverse)
#ugly ass file path, but will deal with later
coinmetric_data = read_rds("../../../Coincept/data/coinmetric_data.rds")


df = coinmetric_data %>% 
  select(date, result, metric) %>% 
  filter(metric %in% c("exchangevolume(usd)", "txvolume(usd)"))  %>% 
  spread(metric, result) %>% 
  set_names(snakecase::to_snake_case) %>% 
  mutate(exchange_over_volume = exchangevolume_usd / txvolume_usd)

```

This gives us a dataset with all these metrics for a year since we set `start_date` to year. There's also a `number_of` argument in the `to_unix` function so you can just do `start_date = to_unix("year", number_of = 5)` to get the last 5 years of data or whatever.  
```{r data look}
unique(coinmetric_data$metric)
```

#Initial plots 

To be honest, I'm not sure how to really look at this. Just a couple rough ass plots because I don't have time rn. It's complicated since we have three metrics (both volumes and then time).

```{r plots, fig.align='c', fig.width=8, fig.height=6}
df %>% 
  ggplot(aes(
    x = date,
    y = exchange_over_volume
  )) + 
  geom_line() + 
  # geom_point() +
  # geom_line(aes(
  #   group = date
  # )) + 
  theme_light() + 
  ggtitle("exchange_over_volume")
```

```{r plots2, fig.align='c', fig.width=8, fig.height=6}
df %>% 
  gather(metric, result, ends_with("_usd")) %>% 
  ggplot(aes(
    x = date,
    y = result,
    group = metric
  )) + 
  geom_line(aes(
    color = metric
  )) + 
  #scale_y_continuous(scales::comma)  + 
  theme_light() + 
  ggtitle("exchange and volume") + 
  theme(legend.position = "bottom")

```




<!-- ##Code appendix -->
<!-- ```{r code = readLines(knitr::purl(rmd)), echo = TRUE, eval=FALSE} -->
<!-- #paste all R code used down here -->
<!-- ``` -->